
\begin{abstract}
本文提出了一个全新的系统架构原型设计―基于贝叶斯分类的多算法混合调度平台（Mixed-algorithm Scheduling Platform Based on Bayes-Classifier，简称$MSPB^2C$），目的是在虚拟计算平台下给出一种任务资源请求的最佳组态。

虽然硬件技术的发展非常迅速，但是相比不断膨胀的需求，资源显得还是有限的，虚拟资源调度系统追求的目的就是寻找一种分配策略从而最大化的满足各个请求的需求，并使得该分配方案获得时空上的最优。在$MSPB^2C$系统中，设计了一种基于数据挖掘分类技术的预测机制，以实现对任务请求的分类划分，获得更好的组合方式。为了更加快速地做出决策，采用了模式完整下的一种最优分类器―贝叶斯分类器。为了能够具有自适应的特点，设计了一个评价因子，对一次决策过程的结果进行比较，反馈给预测和分类模块，用于信息的存储交换，以便下次做出更好的决策。

本系统解决了目前系统不能具有学习和自适应能力的缺点，使系统具有描述状态信息的同时具有预测的能力，以更好的方式实现了资源请求的合理调度。通过测试评估，该方案可为虚拟计算平台提供较为智能的决策支持。

\keywords{虚拟化，资源分配，贝叶斯分类}
\end{abstract}

\begin{englishabstract}
A novel prototype of system architecture-Mixed-algorithm Scheduling Platform Based on Bayes-Classifier,namely $MSPB^2C$,is proposed in this paper,aiming to give a best configuration of task's resources request under the virtual computing platform.

Although the hardware technology develops very quickly,compared to growing demand, resources are still limited, therefore the pursuit of Virtual Resources Scheduling System is to find a scheduling policy that maximize the meet to the needs of individual requests, and so that the assignments given are spatial and temporal optimal. In the $MSPB^2C$ system, designing a prediction mechanism based on data mining classification technology to achieve division of category to tasks' requests,and get a better combination. In order to make a fast decision,an optimal classifier under the circumstance of full pattern-Bayes classifier is adopted.For the adaptive characteristics, designing an evaluation factor, comparing the results to a decision-making process, thus the feedback will send to prediction and classification modules for exchanging storage-information, so that a better decision will be made.

This system addresses the current systems' disadvantage of learning and adapting, making the system has the ability to describe the status information and to make a prediction,simultaneously,a reasonable scheduling of resources requests thereupon is achieved in a better way.Through testing and evaluation,this programme can be more intelligent in decision-making support on virtual computing platforms.

\englishkeywords{virtualization,resources allocation,Bayes classification}
\end{englishabstract}

