
\fontsize{10.5pt}{10.5pt}\selectfont
\begin{thebibliography}{10}

\bibitem{Strachey}
 Strachey C.
\newblock {Time Shring in Large Fast Computers[A]}.
\newblock In International Conference on Information Processing(1959).

\bibitem{CloudCompCodec}
雷葆华，饶少阳，江峰 等.
\newblock {云计算解码[M]}.
\newblock 电子工业出版社(2011.4).

\bibitem{intro_algorithm}
 Mark Stillwell,David Schanzenbach,Viven F.
\newblock {Resource Allocation Algorithm for Virtualized Service Hosting Platform[J]}.
\newblock Journal of Parallel and Distributed Computing(2010).

\bibitem{intro_SJSU}
 Shailesh Sawant
\newblock {A Genetic Algorithm Scheduling Approach for Virtual Machine Resources in a Cloud Computing[J]}.
\newblock San Jose State University Master's Theses and Graduate Research(2011).

\bibitem{intro_probabilistic}
Richard M.,Michael Luby.
\newblock {A Probabilistic Analysis of Multidimensional Bin Packing Problems}.
\newblock University of California at Berkeley,University of Toronto,University di Roma,ACM(1984).

\bibitem{intro_probabilistic_theta}
Ekow,Ali Pinar,Doron Rotem.
\newblock {A $\Theta$(n) Approximation Algorithm for 2-Dimensional Vector Packing}.
\newblock Lawrence Berkeley National Laboratory,Sandia National Laboratory(1984).

\bibitem{intro_DRF}
Ali Ghodsi, Matei Zaharia, Benjamin Hindman.
\newblock {Dominant Resource Fairness: Fair Allocation of Multiple Resource Types[R]}.
\newblock University of California, Berkeley .MESOS Project(2011).

\bibitem{intro_BMDKP}
Xin Sun,Sen Su,Peng Xu.
\newblock {Multi-dimensional Resource Integrated Scheduling In a Shared Data Center[J]}.
\newblock 31st International Conference on Distributed Computing Systems Workshops(2011).

\bibitem{intro_EUCAL}
Daniel Nurmi,Rich Wolski,Chris Grzegorczyk.
\newblock {The Eucalyptus Open-Source Cloud-Computing System}.
\newblock University of California,SB.

\bibitem{intro_nebula}
Open Nebula.
\newblock http://www.opennebula.org

\bibitem{intro_openstack}
Openstack.
\newblock http://openstack.org

\bibitem{VMware}
VMware.
\newblock http://www.vmware.com/cn/

\bibitem{wiki}
维基百科中文.
\newblock http://zh.wikipedia.org/wiki/Wikipedia:虚拟化

\bibitem{ibm_virtual_his}
IBM虚拟化发展史.
\newblock http://www-900.ibm.com/cn/itmanager/virtualization/solutions/\\virtualization/history.shtml

\bibitem{camxen}
Xen,University of Cambridge.
\newblock http://www.cl.cam.ac.uk/research/srg/netos/xen/.

\bibitem{VMwareInfrastructure}
VMware Infrastructure.
\newblock http://www.vmware.com/products/vi/overview.html.

\bibitem{libvirtsite}
Libvirt Virtualization API.
\newblock http://libvirt.org/.

\bibitem{data}
Hand D,Mannila H,Smyth P.
\newblock {Principles of Data Mining[M]}.
\newblock {(2002)}.

\bibitem{MinErrBayes}
福永奎之介 著,陶笃纯 译.
\newblock {统计图形识别导论[M]}.
\newblock {科学出版社(1978)}.

\bibitem{Saridis}
Saridis G N,Valavanis K P.
\newblock {Mathematical Formulation for the Organization Level of Intelligence Machines[M]}.
\newblock {Proc.Conference of Robotics and Automation,San Francisco,CA,Apr(1986,4:267-272)}.

\bibitem{KLR98}
Ruby L,Kennedy ,Yuchun Lee.
\newblock {Solving Data Mining Problems Through Pattern Recognition[M]}.
\newblock {Englewood Cliffs,N,J.:Prentice Hall}.

\bibitem{Datamining}
Margaret H.Dunham.
\newblock {Data Mining Introductory and Advanced Topics[M]}.
\newblock Chap3,4.Pearson Education,(2006).


\bibitem{Weka}
Weka.
\newblock http://www.cs.waikato.ac.nz/ml/weka/.

\bibitem{dataclass}
刘伯成，陈庆奎.
\newblock {云计算中的集群资源模糊聚类划分模型[J]}.
\newblock 《计算机科学》10A，卷38，(2011).
\end{thebibliography}
